Software Citation Principles

### 2016-02-10 sc-principles/software-citation-principles.tex
adding bib doc and cite to data citation principles, fixing order of abstract and maketitle...

\begin{document}
\maketitle

@@

@@

\katznote{The initial context of this section is liberally borrowed and loosely adapted from \url{https://www.force11.org/group/joint-declaration-data-citation-principles-final}}

@@

>>>>

\begin{document}

@@

\maketitle

@@

\katznote{The initial context of this section is liberally borrowed and loosely adapted from \cite{data-citation-principles}}

@@

\bibliographystyle{abbrv}
\bibliography{software-citation-principles}
